salad

### 2025-02-17 inst/salad.Rmd
distinguish hankin2017 from hankin2017_rnw
incorporate Heather Turner's work

---
title: "salad"
output: bookdown::html_document2
author: "R. K. S. Hankin"
bibliography: hyper2.bib
---

@@

To cite the `hyper2` package in publications, please use @hankin2017.
This short document shows how to apply `hyper2` idiom to the `salad`
dataset of the `prefmod` package [@hatzinger2012].  From `salad.Rd`:

@@

>>>>

---
title: "salad"
output: bookdown::html_document2
author: "R. K. S. Hankin"
bibliography: hyper2.bib  # copy vignettes/hyper2.bib to inst/
---

@@

To cite the `hyper2` package in publications, please use @hankin2017_rmd.
This short document shows how to apply `hyper2` idiom to the `salad`
dataset of the `prefmod` package [@hatzinger2012].  From `salad.Rd`:

@@

# Acid analysis

Turner goes on to assess whether a model of tartness using acetic and
gluconic acids is appropriate.  This is possible using the `hyper2`
formalism as follows.

```{r}
features <- data.frame(salad = LETTERS[1:4],
                       acetic = c(0.5, 0.5, 1, 0),
                       gluconic = c(0, 10, 0, 10))
features
(M <- as.matrix(features[,-1]))
makestrengths <- function(v){
    out <- exp(M %*% v)
    out <- c(out/sum(out))
    out <- pmax(out,0)
    names(out) <- LETTERS[1:4]
    return(out)
}
makestrengths(c(2,1))
f <- function(v){loglik(makestrengths(v),H2)}
(maxo <- optim(par=c(3, 0.3), fn=f,control=list(fnscale = -1)))
makestrengths(maxo$par)
loglik(makestrengths(maxo$pa),H1)
maxp(H1,give=1)
```
